{\boldmath Pseudoscalar top-Higgs coupling: Exploration of $\mathrm{CP}$-odd observables to resolve the sign ambiguity }

### 2016-03-09 Paper_ttbarH_Draft.tex
KK: small edit at the end of Sec. IV

The mean values of $\epsilon_8$ for the scenarios under
consideration are comparable with the values listed in Table
\ref{table6} for $\epsilon_5$. Concerning the associated angular
distributions, their range of variation {\bf (KK: I'm not sure what
  this means)} is larger than in the case of
the distributions related to $\epsilon_5$-$\epsilon_7$ but exhibit
smaller changes in their shapes for the different scenarios and for
this reason we do not include here the corresponding plots.
{\bf (KK: might need to reword this a bit after clarifying what 
  range of variation means.)}
\begin{table}[H]
\caption{Asymmetry for the TP $\epsilon_{8}$ for the SM case and the
  two $\mathrm{CP}$-mixed cases defined by $\kp=1,\kpt=\pm 1$. The
  values are obtained with $10^5$ simulated events.}
\label{table8}
\begin{center}
\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}|C{2cm}|}
%\begin{tabular}{|c|r||r|c||r|c||r|c|}
\hhline{|====|}
%\hhline{|--------|}
$\kappa_t$&$\tilde{\kappa}_t$~~&$\mathcal{A}(\epsilon_8)$~~&$\mathcal{A}(\epsilon_8)/\sigma_{\mathcal{A}}$ \\ 
\hhline{|====|} 
%\hhline{|--------|}
$1$ & $-1$~~~ & $0.0331$~ & $10.5$~ \\[0.6mm]
\hline
$1$ & $0$ & $0.0023$~ & $0.7$~ \\[0.6mm]
\hline
$1$ & $1$ & $-0.0403$~~~ & $\,-12.7$~~~~ \\[0.6mm]
\hhline{|====|}
%\hhline{|--------|}
\end{tabular}
\end{center} 
\end{table}
\section{{\boldmath{$\mathrm{CP}$}}-odd observables not depending on \MakeLowercase{{\boldmath $t$}} and \MakeLowercase{{\boldmath $\tbar$}} momenta}
\label{sec5}
The observables discussed in the preceding sections all involve the
momenta of the top and/or anti-top quarks and thus require the full
reconstruction of the kinematics of the individual $t$ and $\tbar$
systems in order to be measured. Although challenging due to the
presence of the two neutrinos in the final state, this can in principle be
done by applying a kinematic reconstruction method such as the
neutrino weighting technique~\cite{atlasconf,atlascharge}. Another
possibility is to define observables that do not depend on the $t$
and $\tbar$ momenta but instead make use of the momenta of the
$b$ and $\bbar$ quarks to which the $t$ and $\tbar$ decay. In
order to construct such observables we will take as our starting
point the most
sensitive observables studied in Secs.~\ref{sec3} and \ref{sec4},
namely those associated with the TPs $\epsilon_4$ and $\epsilon_8$,
respectively.

>>>>

The mean values of $\epsilon_8$ for the scenarios under
consideration are comparable with the values listed in Table
\ref{table6} for $\epsilon_5$.
We have also studied the associated angular distributions.
We do not include plots of these distributions, however,
because they
do not exhibit much visible variation for the different
scenarios under consideration.  (The situation is similar
to that encountered for the angular distribution
associated with $\epsilon_4$ -- see the discussion
at the end of Sec.~\ref{sec3.2}.)
{\bf (KK: have I worded this correctly?
  Does the distribution look similar even in the
  purely CP-odd case, for example?)}

\begin{table}[H]
\caption{Asymmetry for the TP $\epsilon_{8}$ for the SM case and the
  two $\mathrm{CP}$-mixed cases defined by $\kp=1,\kpt=\pm 1$. The
  values are obtained with $10^5$ simulated events.}
\label{table8}
\begin{center}
\begin{tabular}{|C{1cm}|C{1cm}||C{2cm}|C{2cm}|}
%\begin{tabular}{|c|r||r|c||r|c||r|c|}
\hhline{|====|}
%\hhline{|--------|}
$\kappa_t$&$\tilde{\kappa}_t$~~&$\mathcal{A}(\epsilon_8)$~~&$\mathcal{A}(\epsilon_8)/\sigma_{\mathcal{A}}$ \\ 
\hhline{|====|} 
%\hhline{|--------|}
$1$ & $-1$~~~ & $0.0331$~ & $10.5$~ \\[0.6mm]
\hline
$1$ & $0$ & $0.0023$~ & $0.7$~ \\[0.6mm]
\hline
$1$ & $1$ & $-0.0403$~~~ & $\,-12.7$~~~~ \\[0.6mm]
\hhline{|====|}
%\hhline{|--------|}
\end{tabular}
\end{center} 
\end{table}
\section{{\boldmath{$\mathrm{CP}$}}-odd observables not depending on \MakeLowercase{{\boldmath $t$}} and \MakeLowercase{{\boldmath $\tbar$}} momenta}
\label{sec5}
The observables discussed in the preceding sections all involve the
momenta of the top and/or anti-top quarks and thus require the full
reconstruction of the kinematics of the individual $t$ and $\tbar$
systems in order to be measured. Although challenging due to the
presence of the two neutrinos in the final state, this can in principle be
done by applying a kinematic reconstruction method such as the
neutrino weighting technique~\cite{atlasconf,atlascharge}. Another
possibility is to define observables that do not depend on the $t$
and $\tbar$ momenta but instead make use of the momenta of the
$b$ and $\bbar$ quarks to which the $t$ and $\tbar$ decay. In
order to construct such observables we will take as our starting
point the most
sensitive observables studied in Secs.~\ref{sec3} and \ref{sec4},
namely those associated with the TPs $\epsilon_4$ and $\epsilon_8$,
respectively.
